### 2008-03-17 SAiP/Module1/H3/doc/qualityattributes.tex
Finishing Quality attributes

\fixme{Answer question 3.3}

@@

\fixme{Answer question 3.4}

@@

\fixme{Answer question 3.5}

>>>>

As we have all experience the irritation of a slow web-site, and as the competition on the internet is growing, it is important to achieve propper performance.

Due to the lowing price of hardware and the increasing price of developement time, it is often cheapest and certainly simper to use the tactic \emph{Increase available resourcez}; introduce load balancing with multiple parallel servers thereby increase performance during heavy-load situations, ensure that the serves have sufficient network bandwidth, RAM and CPU strength to handle many simultanious database look-ups - here the tactic of \emph{Maintain multiple copies of data or computations} may be used to speed up database-look-up by caching the most popular searches, or cach the entire result in preperation for a search refinement. If the database is remotely located the caching of results becomes even more important.

There are many other tactics which may be employed, yet given the nature to the application, it is not believed that the biggest resource consumers are under developement control, for building the web-server from scratch to support better concurrency or using non-standard performance tweaking algorithms for the database-lookup, will most likely become inconcivably expensive compare to simply increasing the computational resources.

@@

As SOA is all about standardised interfaces supplying a functionality which may be used by many different products, the areas where SOA makes sens is naturally between teh components.

Instead of creating a web-server which access a database through a specific facade, one may argue whether the desired functionality may not be generalised. "Look-up in database". This may easily be hidden behind a standardised service, e.g. a web-service, meaning that anyone on the WWW who supplies a batabase service may be used to host the beer database, and if one becomes dissatisfied with the database provider, it is transparent to simply switch to another.

Taking this one step further, perhaps the database service may be extended with a data-base type, meaning that the Beer Web Store's domain model is exposed in a service, which would allow for not only displaying ones own brands of beer, but through a discovery service, also beer-brands by other brewers on the net who implement this service. This will also point the way for a more standardised lookk-and-feel when shopping for beer.

Naturally just because a web-service (or other service) is used it does not mean that it has to be public, jet it does have some advabtages.

Finally the WS-Security web-service may be used to handle payment, and also possibly, if the database or Beer Web Store Domain model is exposed through a web-service, it may also be benificial that not everyone may have the ability to update the domain model or database, so here the WS-Security service may also come in handy.

Naturally this generality do not necesarrliy come free. A look-up in a database behind a service, especially a web-service, is far slower than a direct look-up in a local database, thereby influencing Performance poorly. On the other hand the use of web-services may increase Availability, as the functionality is deployed on multiple servers, thereby redusing the chance of the system becomming fully non-responsive. Naturally the critical path must be evaluated, as if a link on the critical path chain become non-responsive then the entire system becomes non-responsive.

@@

The quality attributes are vital to the software architecture, as they not only define the requirements to the software architecture (along with the scenarios), but also describe their relative importance. The quality attributes therefore allow the architecture the be evaluated in terms of how well it supports or enables a system's desired external (e.g. availability and performance) and internal behaviour (e.g. testability and modifiability). \cite{h_sarjoughian2002}
